Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-03 supp.rnw
Add a line to the partial residual plots showing the fitted alpha value.

	partial_residual_plot <- function(parameters, species_output_order) {
		plot_df <- c()
		for(row_index in 1:num_species) {
			for(col_index in 1:num_species) {
				temp_df <- data.frame(
					y = input_data$get_partial_residuals(parameters, row_index, col_index),
					x = input_data$get_partial_residuals_x(row_index, col_index)
				)
				temp_df$row_index <- rep(row_index, nrow(temp_df))
				temp_df$col_index <- rep(col_index, nrow(temp_df))
				plot_df <- rbind(plot_df, temp_df)
			}
		}

@@

		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = x, y = y)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::facet_grid(row_species~col_species) +
			ggplot2::labs(x = "Number of individuals of competing species", y = "Partial residual growth rate of focal species (per capita)") +
			ggplot2::theme(strip.text = ggplot2::element_text(size=7))
		return(plot)
	}

@@

\newcommand\modelfitplotcaption[1]{%
	\caption{%
		Plot of model fit using the #1.
		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
		The black line shows $y=x$.
	}%
}
\newcommand\partialresidualplotcaption[1]{%
	\caption{%
		Partial residual plots showing the effects of competition coefficients in the #1.
		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
	}%
}

>>>>

	partial_residual_plot <- function(parameters, species_output_order) {
		plot_df <- c()
		for(row_index in 1:num_species) {
			for(col_index in 1:num_species) {
				temp_df <- data.frame(
					y = input_data$get_partial_residuals(parameters, row_index, col_index),
					x = input_data$get_partial_residuals_x(row_index, col_index)
				)
				temp_df$row_index <- rep(row_index, nrow(temp_df))
				temp_df$col_index <- rep(col_index, nrow(temp_df))
				temp_df$alpha <- parameters$alpha_values[row_index, col_index]
				plot_df <- rbind(plot_df, temp_df)
			}
		}

@@

		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = x, y = y)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::geom_abline(ggplot2::aes(slope = alpha, intercept = 0)) +
			ggplot2::facet_grid(row_species~col_species) +
			ggplot2::labs(x = "Number of individuals of competing species", y = "Partial residual growth rate of focal species (per capita)") +
			ggplot2::theme(strip.text = ggplot2::element_text(size=7))
		return(plot)
	}

@@

\newcommand\modelfitplotcaption[1]{%
	\caption{%
		Plot of model fit using the #1.
		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
		The black line shows $y=x$.
	}%
}
\newcommand\partialresidualplotcaption[1]{%
	\caption{%
		Partial residual plots showing the effects of competition coefficients in the #1.
		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
		The black line shows, by its slope, the alpha value fitted by the model.
		The blue line shows a linear regression fitted to the plotted points, with \SI{95}{\percent} confidence interval.
	}%
}
